\documentclass[10pt,a4paper,sans, colorlinks]{moderncv}

\moderncvcolor{black}
\moderncvstyle{banking}


\usepackage[scale=0.86, top=1.2cm, bottom=1.2cm, left=1.2cm, right=1.2cm]{geometry}
\recomputelengths

\usepackage{fontawesome}
\usepackage{wasysym}
\usepackage{fontspec}

%Select fonts
\setsansfont[Ligatures=TeX, Numbers=OldStyle]{Concourse T3 Tab}

\firstname{Nikhil}
\familyname{N}

\title{CV}
\address{Software Development Engineer 3}
\mobile{+917676295696} 
\email{chintun1988@gmail.com}
\AtBeginDocument{
    \hypersetup{colorlinks,urlcolor=purple}
}

\begin{document}

\makecvtitle

\vspace{-12 mm}

\section{Summary}

\small{A software engineer experienced in building high quality software products and solutions from end to end and capable of working in a fast paced dynamic environments. I am interested in developing scalable, performant, high quality frontend and backend applications.}

\section{Education}

\cventry{}{}{International Institute of Information Technology, Bangalore}{M.Tech, Information Technology}{}{}
\vspace{-4.5 mm}
\cvitem{\small{Key Courses}}{\small{Algorithms, Data Structures, Operating Systems, Object Oriented Analysis and Design, Database Systems}\normalsize{}}
\cvdoubleitem{Scores}{3.37/4}{Awards}{Directors merit list student}

\section{Interests \& Expertise}

\begin{itemize}
\item Interested in learning new innovations in software systems design which focuses on scale and performance.
\item Interested in design and implementation of software products from end to end (frontend and backend)
\item Interested in learning new trends in design of large scale distributed systems.
\item Experienced in developing full stack web and mobile applications.
\item Experienced in developing cross platform mobile applications with focus on quality and reuseability.
\item Experienced in leading small teams \& mentoring team members, contributing to technology, product \& process initiatives.
\end{itemize}

\section{Skills}
\cvitem{Languages}{C, C++, Java, Javascript}
\cvitem{\small{Libraries \& Frameworks}}{\small{Reactjs, mobx, Spring}\normalsize{}}
\cvitem{Databases}{MySQL, DynamoDB}
\cvitem{Tools}{Maven, Gradle \& CMake}
\cvitem{Version Control}{Perforce \& GIT}


\section{Experience}

\cventry{March, 2015 -- Present}{Computer Scientist}{Adobe}{Bengaluru, India}{}{}\normalsize\vspace{-2mm}

\begin{itemize}
\item \textbf{Adobe Notification System (ANS)} : ANS lets Adobe apps \& services deliver device-oriented notifications to Adobe users reliably across desktop, web and mobile in real-time with minimal integration effort. It's been extensively used by more than 65+ adobe creative, experience and document cloud products. I currently own various features which include sending Group Notifications, Delivery pipeline, real time alerts, localisation support. I have also redesigned and implemented the frontend for the service in reactjs and redux to cater to experience cloud use cases. Technologies: Java, Amazon Web Services (DynamoDB, S3, SNS, Lambda, SQS, RDS, CloudWatch etc), Spring framework, Netflix open source libraries (Hystrix), Redis.
\item \textbf{Project Gemini} : Gemini is a next generation drawing and painting app that combines the capabilites of both Adobe Draw and Adobe Sketch. I worked on a backend service that converts Draw and Sketch projects into Gemini compatible format. Handling this conversion at a large scale and outburst traffic patterns was a challenge to solve.
\item \href{https://play.google.com/store/apps/details?id=com.adobe.creativeapps.draw}{\faAndroid\hspace{1mm}Adobe Draw}: A professional painting and drawing from adobe trageted for large handheld devices like tablets. I worked on core features like drawing editor, brush and toolbar panels, layers editor, projects organiser, synchronising assets with Creative Cloud.
\item \href{https://play.google.com/store/apps/details?id=com.adobe.creativeapps.shape}{\faAndroid\hspace{1mm}Adobe Shape}: Design and implementation of major portions of the app. Interacting with the shape generation library and workflows to save generated assets to Creative Cloud were the major contributions.
\end{itemize}

\cventry{August, 2014 -- Feb, 2015}{MTS 2}{\textsc{NetApp}}{Bengaluru, India}{}{}\normalsize\vspace{-2mm}
\begin{itemize}
\item Software developer working in Flex Array Virtualization (FAV)
team.
\item Work involved in developing storage stack which virtualizes and allows customers to attach third party storage systems to our storage system.
\end{itemize}

\cventry{July, 2012 -- July, 2014}{Software Developer}{\textsc{Texas Instruments}}{Bengaluru, India}{}{}\normalsize{}\vspace{-2mm}
\begin{itemize}
\item A software framework developer for the next generation TI SOC platforms
\item The framework allows customers to quickly prototype and evaluate vision algorithms and create custom data flows involving Video capture, Video Processing and Video Display.
\item Worked extensively in developing plug and play components in C/C++.
\end{itemize}
\cventry{\small{Feb, 2012 -- June, 2012}}{\small{Software Development Intern, IBM India Software Labs}}{IBM}{Bengaluru, India}{}{}\normalsize{}
Worked in AIX Performance tools development team. I was involved in developing tools that display statistics related to the four main subsystems of AIX operating system namely CPU, Memory, Disk and Network.


\end{document}
