\documentclass[10pt,a4paper,sans, colorlinks]{moderncv}

\moderncvcolor{black}
\moderncvstyle{banking}


\usepackage[scale=1, top=0.5cm, bottom=0.5cm, left=1.2cm, right=1.2cm]{geometry}
\recomputelengths

\usepackage{fontawesome5}
\usepackage{wasysym}
\usepackage{fontspec}

%Select fonts
\setsansfont[Ligatures=TeX, Numbers=OldStyle]{Concourse T3 Tab}

\firstname{Nikhil}
\familyname{Neela}

\title{Resume}
\address{Backend Software Engineer}
\mobile{+919972059922} 
\email{nikhilneela@gmail.com}
\social[linkedin][www.linkedin.com/in/nikhilneela]{nikhilneela}
\AtBeginDocument{
    \hypersetup{colorlinks,urlcolor=purple}
}

\begin{document}

\makecvtitle

\vspace{-12 mm}

\section{Summary}

\small{A software engineer experienced in building high quality software products and solutions from end to end and capable of working in a fast paced dynamic environments. I am interested in developing scalable, performant, high quality backend applications. }

\section{Education}

\cventry{}{}{International Institute of Information Technology, Bangalore}{M.Tech, Computer Science}{}{}
\vspace{-4.5 mm}
\cvitem{\small{Key Courses}}{\small{Algorithms, Data Structures, Operating Systems, Object Oriented Analysis and Design, Database Systems}\normalsize{}}

\section{Interests \& Expertise}

\begin{itemize}
\item Interested in learning new innovations in software systems design which focuses on scale and performance.
\item Interested in learning new trends in design of large scale distributed systems.
\item Experienced in handling large scale distributed systems.
\item Experienced in leading small teams \& mentoring team members, contributing to technology, product \& process initiatives.
\end{itemize}

\section{Experience}

\cventry{March, 2020 -- Present}{Senior Software Engineer}{Microsoft}{Hyderabad, India}{}{}\normalsize\vspace{-2mm}

\begin{itemize}
\item \textbf{Azure App Services} : Azure App Service is a fully managed PaaS offering that enables developers to build, deploy and scale web apps and APIs quickly. As a engineer in control plane, I own various features which include Deployment Slots, API throttling, DNS management, Backup and Restore
\item \textbf{Deployment Slot Swaps} : Revamped deployment slot swap feature by introducing a state machine with Durable Task Framework, resolving instability issues and minimizing customer-reported incidents. The redesign ensures persistent state-saving during interruptions, contributing to a more robust and reliable deployment process. Successfully mitigated on-call challenges, significantly enhancing overall customer satisfaction. Technologies : C\#.Net, Azure SQL
\item \textbf{API Throttling} : Developed a flexible API throttling module for control plane, offering effective protection against service abuse. The highly adaptable module, with customizable parameters, has been widely adopted by multiple teams, showcasing its versatility and success in safeguarding services. Technologies : C\#.Net, Azure Redis, Azure SQL, IIS
\item \textbf{DNS Management} : Led a seamless migration of Azure App Services DNS entries from an overloaded zone to a new system, ensuring zero downtime. Also implemented regionalized DNS endpoints to eliminate Single Point of failure. Technologies : C\#.Net, Azure DNS, Quartz.NET
\item \textbf{Backup and Restore} : As part of BCDR, I have designed and implemented Backup and Restore of app service allowing customers to backup and restore web applications easily. Additionally customers can clone a running app to a new app or a deployment slot for testing and staging purposes. This feature, extensively utilized in Azure App Services on a daily basis, provides invaluable support by enabling users to swiftly revert changes in case of application issues. Technologies : C\#.Net, Azure Event Grid, Azure SQL 
\item Apart from these, I also maintain existing feature and solve customer incidents (servicing loops) by debugging using in house tools like Azure Data Explorer (Kusto), App Lens \& Observer 
\end{itemize}

\cventry{March, 2015 -- Feb, 2020}{Computer Scientist-2}{Adobe}{Bengaluru, India}{}{}\normalsize\vspace{-2mm}

\begin{itemize}
\item \textbf{Adobe Notification System (ANS)} : ANS lets Adobe apps \& services deliver device-oriented notifications to Adobe users reliably across desktop, web and mobile in real-time with minimal integration effort. It's been extensively used by more than 65+ adobe creative, experience and document cloud products. I owned various features which include sending Group Notifications, Delivery pipeline, real time alerts, localisation support. I have also redesigned and implemented the frontend for the service in reactjs and redux to cater to experience cloud use cases. Technologies: Java, Amazon Web Services (DynamoDB, S3, SNS, Lambda, SQS, RDS, CloudWatch etc), Spring framework, Netflix open source libraries (Hystrix), Redis.
\end{itemize}

\cventry{August, 2014 -- Feb, 2015}{Member of Technical Staff}{\textsc{NetApp}}{Bengaluru, India}{}{}\normalsize\vspace{-2mm}
\begin{itemize}
\item Software developer working in Flex Array Virtualization (FAV)
team.
\item Work involved in developing storage stack which virtualizes and allows customers to attach third party storage systems to our storage system.
\end{itemize}

\cventry{July, 2012 -- July, 2014}{Software Developer}{\textsc{Texas Instruments}}{Bengaluru, India}{}{}\normalsize{}\vspace{-2mm}
\begin{itemize}
\item A software framework developer for the next generation TI SOC platforms
\item The framework allows customers to quickly prototype and evaluate vision algorithms and create custom data flows involving Video capture, Video Processing and Video Display.
\item Worked extensively in developing plug and play components in C/C++.
\end{itemize}
\cventry{\small{Feb, 2012 -- June, 2012}}{\small{Software Development Intern, IBM India Software Labs}}{IBM}{Bengaluru, India}{}{}\normalsize{}
Worked in AIX Performance tools development team. I was involved in developing tools that display statistics related to the four main subsystems of AIX operating system namely CPU, Memory, Disk and Network.


\end{document}
